`r title`

### 2018-01-31 lib/report.Rmd
progress

Contraband found: `r contraband_found_pct`

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
```

>>>>

Contraband found (all stops): `r contraband_found_pct`

Contraband found (where search conducted): `r predicated_contraband_found_pct`

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
predicated_contraband_found_by_race_plot
if (exists("predicated_contraband_drugs_by_race_plot")) {
  predicated_contraband_drugs_by_race_plot
}
if (exists("predicated_contraband_weapons_by_race_plot")) {
  predicated_contraband_weapons_by_race_plot
}
```
